Anonymous provision of local services via blockchain

### 2022-02-24 access.tex
docs: update

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

@@

\subsection{Use cases}
\paragraph{Anonymous clinical tests} \label{anonymous-clinical-tests}

Patients willing to take a steroid test, drug tests, venereal diseases
test, paternity test — have strong incentive to keep the whole
procedure private. Merely the fact that they took the test — without
exposing the results — is suggestive enough to act as a premise in
case of a conflict.

Especially celebrities, politicians and public persona are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their materials and results are stored
securely and kept in private from any unauthorised actor (both
curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.

\paragraph{Anonymous lawyer consultations} \label{anonymous-lawyer-consultations}

People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.

@@

Our protocol would allow taking such advices anonymously, and therefore
getting rid of the strong trust assumption put on the laboratories and
their IT systems.

\subsection{Contribution}
We contribute to the field of fair-exchanges by proposing a simple,
practical, and strongly anonymous framework that does not rely on
centralised trusted-third party, but on decentralised blockchain and
distributed content addressable networking.

@@

Our framework simultanesly provides three main properties:

@@

Next, both Alice and Bob exchange the sets of encrypted key shares with
each other. And send funds to the escrow account.

@@

However, the system doesn't achieve full anonimity but pseudonimity (see
section~\ref{pseudo-anon}). Also the protocol does not
cover the case of dispute between the parties.

@@

Such decentralised, voluntary, and anonymous dispute resolution system
might work for simple contracts violation like eBay seller sending
broken or wrong product, or Airbnb apartment being not adequate to the
photos in the offer. However it's hard to realise such decentralised
evaluation of quality of heath or legal services when expertise and
privacy concerns are taken into an account. Therefore, in our protocol
we take the more conservative approach and resolve disputes using local
justice system (police or court).

@@

\subsection{Proof to justice}\label{proof-of-justice}
In case of dispute the customer can proof to the justice (police, court,
etc.) evidences that convinces the justice about the honesty of customer
and misbehaviour of SP. The reason why the SP can not start a dispute is
that the customer is anonymous, and therefore there is no personal
information to start a dispute against. To mitigate this issue the SP is
always in advantaged postition, so that he has no reason to start a
dispute. The idea described further in section ~\ref{future-work}.

Abstracting from the services the SP is providing, in case of dispute
the customer should be able to prove that: (i) he delivered to the SP a
complete (according to the SP requirements) package \(pkg\), and the SP
accepted it; (ii) he paid for the transaction \(tx\).

@@

\subsection{Pseudo-anonymous vs anonymous blockchain}

@@

Anonymity is a the ability to hide one identity from others. More precisely, the unability to correlate actions performed within the sytem to the identity of the user. Or we can say, that the system guarantee anonimity if for all observers the actions are equally likely to be associated with any user of the system. However, anonimity is a spectrum rather than dichotomous classification. One method of quantifying level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measure the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users. The larger \textit{k}, the higher anonymity.

@@

The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and unlikability, not via assumption that the connection between an address and the real identity is concealed.

@@

\item
  separate address --- each transaction derives new address uniquely
  associating it with the transaction. Such addresses can be derived
  using BEP-32 standard.
\item
  memo --- the payments are send to one SP account, but contain extra
  field named ``memo'' which contains a random value generated by SP and
  included in POD. Each payment containing such value in memo is
  considered to pay for the transaction in question. in case of dispute,
  the connection can be disclosed by revealing the value in POD and
  payment's memo.
\end{itemize}

@@

In case of a dispute there must a way to prove to the justice that the
customer has paid for the transaction. As the proof of transaction is
trivial in transparent and trackable blockchains, it gets more
complicated when it comes to anonymous blockchains. Monero allows
proving and checking payments via dedicated API \cite{Howtopro46}.
ZCash provides mechanism called Payment Disclosure \cite{AnIntrod25},
which at the time of writing is still a experimental feature
\cite{paymentd11}. Proving payments that were made with the usage of
mixers, involve two steps.

@@

We take the same approach. Once the SP creates the results, he encrypts
them using the previously provided customer's public key; then publish
them into a IPFS network.

@@

\(\mathrm{SP}\) - Service Provider. \(\mathrm{customer}\) - Customer.
\(\mathrm{pkg}\) - package anonymously delivered by customer to SP.
\(\mathrm{materials}\) - materials used by SP to provide services, can
be of any kind: urine, saliva, blood, stool, or health documents, legal
documents etc. \(\mathrm{results}\) - results in binary format, can be
either PDF, docx or any format agreed by both parities. \(\mathrm{PoD}\)
- Proof-of-Delivery is a confirmation issued by SP to the customer after
the \(pkg\) is accepted by the SP. \(\mathrm{PoP}\) -
Proof-of-Provision, a proof of existence of provisioned results.
\(\mathrm{E}_\mathrm{key}(\cdot)\), \(\mathrm{D}_\mathrm{key}(\cdot)\) -
symmetric encryption and decryption operators.
\(\mathrm{S}_\mathrm{key}(\cdot)\), \(\mathrm{V}_\mathrm{key}(\cdot)\) -
digital sign and verify operators. \(\mathrm{sk}\), \(\mathrm{pk}\) -
Key pair of secret and public keys accordingly.
\(\mathrm{DH}(\cdot, \cdot)\) - Diffie--Hellman key exchange. \(CID\) -
Content Identifier, a label used to address content in IPFS.

\subsection{Prerequisites}

Anonymous payments:

\item
  SPs accept packages from unknown customers and give them back
  confirmation of acceptance (to stick with convention we call it
  Proof-of-Delivery).
\item
  SPs accept payment for services via anonymous cryptocurrencies like
  Monero, Grin or ZCash as described in section ~\ref{payment-for-services}.
\item
  Justice accepts as a evidence in dispute proof of payment of
  cryptocurrencies as described in section~\ref{proof-of-justice}.
\end{itemize}

@@

In this section we describe each step of the protocol. The steps are
shown in the figure ~\ref{fig:diagram}.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonser-diagram.png}
\centering
\caption{Diagram}
\label{fig:diagram}
\end{figure}

@@

@@

They protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content. In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$. Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol. Finally, the digital signature $\mathrm{sig}_\mathrm{SP}$ on the $\mathrm{PoD}$ created with the SP's secret key guarantee non-repudiation.

@@

Symbolically: \[
\mathrm{delivery}(\mathrm{pkg}) : \mathrm{PoD}
\]

@@

Symbolically: \[
\mathrm{payment}(\mathrm{PoD}.\mathrm{nonce}) : \mathrm{attestation}
\]

\paragraph{Step 3: Provision of
service}\label{step-3-provision-of-service}

At this point the SP can start the provision of service. If it's
suspicious it may decide to wait until the invoice is paid, otherwise
start immediately.

Symbolically: \[
\mathrm{provision}(\mathrm{pkg}.\mathrm{materials}) : \mathrm{results}
\]

\paragraph{Step 4: Results
publication}\label{step-4-results-publication}

Once the service is finished, some kind of output should be created. The
output should be encrypted using encryption symmetric key provided in
the first step.

The encrypted results can be then published on content network such as
IPFS. As a result, the content identifier (CID) is returned.

Symbolically: \[
 \mathrm{publish}(E_{\mathrm{pkg}.\mathrm{key}}(\mathrm{results})) : \mathrm{PoP}
\]

@@

Now, when the results are published on content addressable network such
as IPFS, the SP publish \(\mathrm{cid}\) obtained in previous step on a
message board doing proof of provision.

Symbolically: \[\mathrm{publish}(\mathrm{cid})\]

@@

Since the delivery and payment was made the customer observes blockchain
for a POP corresponding to his transaction. When it happen,

Symbolically: \[
\mathrm{pull}(\mathrm{pkg.nonce})
\]

\paragraph{Step 7: Results download}\label{step-7-results-download}

Symbolically: \[
\mathrm{download}(\mathrm{cid}) : \mathrm{results}
\]

@@

\subsection{Model}\label{model}

We consider three positions:

\begin{itemize}
\item
  Neutral (•) position is when a party hasn't spend not gain anything of
  significant value (money, time, effort). For example, at beggining of
  the protocol.
\item
  Disadvantage (-) position — when a party has put any effort or paid
  money without being able to reclaim it. In other words it has
  \textbf{risked} its resources. For example, paid for a service in
  advance.
\item
  Advantage(+) position — when a party would benefit if the
  transaction would halt at that point. For example, received payment in
  advance.
\end{itemize}

@@

\item
  Normal --- taking the action prescribed by the protocol.
\item
  Abnormal --- everything that deviates from designed steps of the
  protocol. For example, sending arbitrary message, skipping some step,
  repeating step, timing out.
\end{enumerate}

Moreover, at any step of the protocol the customer can react with two
reactions:

@@

\item
  Agree --- the customer agree with the action and therefore does not
  start a dispute.
\item
  Start a dispute --- the customer does not agree with the action and
  therefore start a dispute.
\end{enumerate}

Therefore, there are two possible actions a party can take at any step
of the protocol and two reactions the customer can take.

Hence, in our analysis we have to consider four different outcomes for
each party of the protocol:

@@

\item
  \(\sigma_\mathrm{n}\) --- after following the protocol within the
  timeframe.
\item
  \(\sigma_\mathrm{d}\) --- after a dispute where the other party hasn't
  broken the protocol.
\item
  \(\sigma_\overline{n}\) --- after not starting a dispute despite the
  other party has broken the protocol.
\item
  \(\sigma_\overline{d}\) --- after a dispute where the other party has
  broken the protocol.
\end{itemize}

The protocol terminate after last step, after starting a dispute, or
after a party hasn't completed it's designated action in time. Therefore
all positions except \(\sigma_\mathrm{n}\) are termination positions.

After starting a dispute, the protocol terminate. After timing out there
is no going back on the normal path.

In our framework, the only party that can start a dispute is the
customer. It's because the customer is anonymous, and so the SP does not
have any personal information to start a dispute against.

To mitigate this issue, the protocol is designed so that the SP who
follows the protocol is always in advantaged position, therefore he has
no incentivisations to start a dispute.

We say that the protocol achieve fairness if:

\begin{align*} 
  \forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} \mathrm{can\ move\ the\ protocol\ \\
  to\ the\ non\ disadvantaged\ position} 
\end{align*}

@@

For the analysis purpose we state assumptions listed below. We consider
them being rational and realistic.

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged
  positions (+). In other words, they have intrinsic motivation to
  initialise the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are available to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in section ~\ref{future-work}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position (-). Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•).
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

@@

\paragraph{Step 1: deliver package}\label{step-1-deliver-package}

Turn: Customer

@@

\paragraph{Step 2: pay for invoice}\label{step-2-pay-for-invoice}

Turn: Customer

@@

\paragraph{Step 3: provision of
service}\label{step-3-provision-of-service}

Turn: SP

SP has done the provision of service:

@@

\paragraph{Step 4: publication of
results}\label{step-4-publication-of-results}

Turn: SP

@@

\paragraph{Step 5: publication of
proof-of-provision}\label{step-5-publication-of-proof-of-provision}

Turn: SP

SP has published proof-of-provision on time:

@@

\paragraph{Step 6: pull
proof-of-provision}\label{step-6-pull-proof-of-provision}

Turn: Customer

@@

\paragraph{Step 7: retrieval of
results}\label{step-7-retrieval-of-results}

Turn: Customer

@@

\subsection{Cryptographically provable availability of
results}\label{cryptographically-provable-availability-of-results}

Currently, the SP has to publish the results into a p2p content storage
network (IPFS). The problem is that, nothing prevent such SP to publish
the content, receive the content identifier (cid), and immediately after
remove it from from it's local storage. In case of dispute the SP can
upload the content again, proving its availability. The SP has no
motivation to proceed with this kind of misbehaviour, other than puting
the customer in disadvantaged position caused by the lost dispute. We see
possible prevention of this misbehaviour by the usage of Filecoin---an
incentive layer on top of IPFS that guarantee the content availability
via economic incentivisations Filecoin~\cite{benetfilecoin}. With the
help of Filecoin, the SP would be obligated to create a Filecoin deal
that guarantee the results availability until the deadline of the
transaction. Moreover, since Filecoin is a blockchain by itself, it
could play both roles of message board and Storage Network.

@@

Without lose of generality the payment can be made with cash. The
customer can exchange the cash with SP together with delivering the
package. The PoD would contain an information that the
transaction has been paid with cash; therefore, Steps 1 and 2 could be
merged together and realised in one step. In case of dispute the payment
disclosure would be in included in PoD.

@@

Currently our framework require customer to deliver the \(pkg\) to SP
personally or via trusted person. However the system could be extended
to support anonymous delivery system as proposed in
Lelantos~\cite{altawy2017lelantos}.

\section{Conclusions}
In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision. The framework can be employed by any local service provider to provide services without collecting any personal information. The payment is handled by anonymous cryptocurrencies, and the results are published on content based p2p network. The dispute can be settled by disclosing proofs to the justice. At any stage of the transaction, both parties are either in privelaged situation or can proof to the justice the misbehaviour of the other party.

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

@@

Example services that would benefit from anonymous services are:
\begin{itemize}
    \item Patients willing to take a steroid test, drug tests, venereal diseases
test, paternity test — have strong incentive to keep the whole
procedure private. Merely the fact that they took the test — without
exposing the results — is suggestive enough to act as a premise in
case of a conflict.

Especially celebrities, politicians and public figures are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorised actor (both curious employee, and malicious attacker).

Our protocol allows taking such tests anonymously and therefore getting
rid of the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take business action that may be risky or not yet fully legislated, may be willing to receive the risk estimation and prediction of possible repercussions of such action.

@@

Our protocol would allow taking such advices anonymously, and therefore
getting rid of the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

We propose a framework for anonymously provisioning services that require delivery of physical materials. A service provider employing our framework can provide services without collecting any personal information from customers.

To achieve these objectives we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a mean for proving that certain actions took place at a certain moment of time without the trusted third party.
    \item Content-addressable peer-to-peer storage network, to provide results to the customer. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

\end{itemize}

We observe that the issue of anonymous service provision can be seen as a problem of fair-exchange where parties exchange some informations in a fairly manner, i.e., either both parties obtain the goods being exchanged, or they both obtain nothing.

In our case the customer is exchanging with the SP cryptocurrency and materials for the results.

We contribute to the field of fair-exchanges by proposing a simple,
practical, and anonymous framework that does not rely on centralised trusted-third party, but on decentralised blockchain and
distributed content-addressable storage network.

@@

Our framework simultaneously provides five main properties:

@@

Next, both Alice and Bob exchange the sets of encrypted key shares with
each other, and send funds to the escrow account.

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see section~\ref{pseudo-anon}). Also, the protocol does not cover the case of dispute between the parties.

@@

Such decentralised, voluntary, and anonymous dispute resolution system
might work for simple contracts violation like eBay seller sending
broken or wrong product, or Airbnb apartment being not adequate to the
photos in the offer. However it's hard to realise such decentralised
evaluation of quality of heath or legal services when expertise and
privacy concerns are taken into an account. Therefore, in our protocol
we take the more conservative approach and resolve disputes using local
justice system (police, court, etc.).

@@

\subsection{Proofs to justice}\label{proof-of-justice}
In case of dispute the customer can proof to the justice (police, court,
etc.) evidences that convinces the justice about the honesty of customer
and misbehaviour of SP. The reason why the SP can not start a dispute is
that the customer is anonymous, and therefore there is no personal
information to start a dispute against. To mitigate this issue the SP is
always in advantaged position, so that he has no reason to start a
dispute. The idea described further in section ~\ref{future-work}.

% Unify with what is writen in fiarness analysis

Abstracting from the services the SP is providing, in case of dispute
the customer should be able to prove that: (i) he delivered to the SP a
complete (according to the SP requirements) package, and the SP
accepted it; (ii) he paid for the transaction.

@@

\subsection{Anonymity, pseudonomity, and confidentality}\label{pseudo-anonymous-vs-anonymous-blockchain}

@@

Anonymity is a the ability to hide one identity from others. More precisely, the unability to correlate actions performed within the system with the identity of the user. Or we can say, that the system guarantee anonymity if for all observers the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than dichotomous classification. One method of quantifying level of anonymity is proposed in \textit{k}-anonymity~\cite{sweeney2002k}. It measure the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users. The larger \textit{k}, the higher anonymity.

@@

The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via assumption that the connection between an address and the real identity is concealed.

@@

\item
  separate address — each transaction derives new address uniquely
  associating it with the transaction. Such addresses can be derived
  using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
\item
  memo — the payments are send to one SP account, but contain extra
  field named ``memo'' which contains a random value generated by SP and
  included in $\mathrm{PoD}$. Each payment containing such value in memo is
  considered to pay for the transaction in question. In case of a dispute,
  the connection can be disclosed by revealing the value in $\mathrm{PoD}$ and payment's memo.
\end{itemize}

@@

In case of a dispute there must a way to prove to the justice that the
customer has paid for the transaction. As the proof of transaction is
trivial in transparent and trackable blockchains, it gets more
complicated when it comes to anonymous blockchains. Monero allows
proving and checking payments via dedicated API \cite{Howtopro46}.
ZCash provides mechanism called Payment Disclosure \cite{AnIntrod25},
which at the time of writing is still a experimental feature
\cite{paymentd11}.

@@

We take the same approach. Once the SP creates the results, he encrypts
them using the previously provided encryption key; then publish
them into a IPFS network.

@@

\subsection{Prerequisites}
We do not design our framework with the particular technologies in mind, instead we state requirements that each party of the framework must satisfy to make the whole system to work together. The choice of the particular technology for each role is up to the implementer.

\begin{itemize}
\item There exists common PKI infrastructure:
    \begin{itemize}
        \item The customer and the SP have their own key pairs consisting of secret key $\mathrm{sk}(\mathrm{party})$ and public key $\mathrm{pk}(\mathrm{party})$, where $\mathrm{party} \in \{\mathrm{C}, \mathrm{SP}\}$ is the customer or the service provider accordingly.
        \item Both the customer and the SP can create and verify digital signatures created by the customer $\mathrm{sig}_{\mathrm{sk}(\mathrm{C})}$ and the SP $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$.
        \item The SP's public key is publicly known.
    \end{itemize}

\item Both the customer and the SP:
    \begin{itemize}
        \item Uses common symmetric encryption $\mathrm{E}_\mathrm{key}(\cdot)$ and decryption $\mathrm{D}_\mathrm{key}(\cdot)$ operations.
    \end{itemize}

\item The SP:
    \begin{itemize}
        \item Accepts packages from unknown customers and give $\mathrm{PoD}$ in return.
        \item Accepts payments with anonymous cryptocurrencies as described in section~\ref{payment-for-services}.
    \end{itemize}

\item Justice:
    \begin{itemize}
        \item Accepts as a evidence in dispute a $\mathrm{PoD}$, $\mathrm{PoP}$, and payment $\mathrm{attestation}$ as described in section~\ref{proof-of-justice}.
    \end{itemize}

\item Anonymous payments:
    \begin{itemize}
        \item Supports anonymous, i.e., untraceable and (ideally) unlinkable transactions as specified in section~\ref{pseudo-anonymous-vs-anonymous-blockchain}.
        \item Supports uniquely identifying transaction either via separate address per transaction, memo field, or other similar mechanism as described in section ~\ref{payment-for-services}. 
    \end{itemize}

\item Message board:
    \begin{itemize}
        \item Supports proofs as large as the size of $\mathrm{PoP}$, i.e., sum size of $\mathrm{cid}$, $\mathrm{nonce}$, and $\mathrm{sig}$.
    \end{itemize}

\item The storage network:
    \begin{itemize}
        \item Allows for uniquely content retrieval via $\mathrm{cid}$ (usually a hash of the content).
        \item Allows for anonymous content retrieval.
    \end{itemize}
\end{itemize}

@@

In this section we describe each step of the protocol. The steps are
shown in the figure ~\ref{fig:protocol-diagram}.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonser-protocol.png}
\centering
\caption{Diagram}
\label{fig:protocol-diagram}
\end{figure}

@@

Symbolically: \[
\mathrm{pkg} \gets (\mathrm{materials}, \mathrm{key})
\]

@@

They protocol starts once the customer delivers package $\mathrm{pkg}$ and the SP accepts its content. In return, the SP issue a $\mathrm{PoD}$ with agreed upfront payment deadline $\mathrm{T}_\mathrm{pay}$, service provision deadline $\mathrm{T}_\mathrm{provide}$ and current time $\mathrm{T}_\mathrm{issue}$. Also, the $\mathrm{PoD}$ consist of randomly generated unique number $\mathrm{nonce}$, which will allow associating all actions related to the transaction throughout the protocol. Finally, the digital signature $\mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}$ on the $\mathrm{PoD}$ created with the SP's secret key $\mathrm{sk}(\mathrm{SP})$ guarantee non-repudiation.

@@

Symbolically: 
\[
\mathrm{PoD} \gets \mathrm{delivery}(\mathrm{pkg})
\]
\[
(\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})}) \equiv \mathrm{PoD}
\]

@@

Symbolically: \[
\mathrm{attestation} \gets \mathrm{payment}(\mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{C})})
\]

\paragraph{Step 3: Provision of
service}\label{step-3-provision-of-service}
Once the transaction is paid the SP start the provision of service.

Symbolically: \[
\mathrm{results} \gets \mathrm{provision}(\mathrm{materials})
\]

\paragraph{Step 4: Results
upload}\label{step-4-results-upload}

After the service is finished, some kind of output should be created. Next, the output is encrypted using encryption symmetric key $\mathrm{key}$ provided in the first step.

The encrypted results are then uploaded on content addressable network such as IPFS. As a result, the content identifier (cid) is returned.

Symbolically: 
\[
\mathrm{cid} \gets \mathrm{upload}(E_{\mathrm{key}}(\mathrm{results}))
\]

@@

When the results are published, the SP perform proof of provision by publishing $\mathrm{cid}$ along with $\mathrm{nonce}$ and signature $\mathrm{sig}_\mathrm{SP}$.

Symbolically: 
\[\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_{\mathrm{sk}(\mathrm{SP})})\]
\[\mathrm{publish}(\mathrm{PoP})\]

@@

After delivering the package and paying for the transaction the customer subscribe to the message board and waits until the SP publish the proof of provision. The subscription is for the SP public key $\mathrm{pk}(\mathrm{SP}$ and transaction's $\mathrm{nonce}$.

Symbolically: \[
\mathrm{cid} \gets \mathrm{subscribe}(\mathrm{pk}(\mathrm{SP}), \mathrm{nonce})
\]

\paragraph{Step 7: Results download}\label{step-7-results-download}
Having the $\mathrm{cid}$, the customer downloads and decrypts the $\mathrm{results}$.

Symbolically: \[
\mathrm{results} \gets \mathrm{D}_{\mathrm{key}}(\mathrm{download}(\mathrm{cid}))
\]

@@

\subsection{Model}\label{model}
We consider three positions:

\begin{itemize}
\item
  Neutral (•) position: when a party hasn't spend nor gain anything of significant value (money, time, effort). For example, at the beginning of the protocol.
\item
  Disadvantage (-) position: when a party has put a significant value without receiving an equivalent. For example, paid for a service in
  advance.
\item
  Advantage(+) position: when a party would benefit if the transaction would halt at that step. For example, the SP has received payment before service provision.
\end{itemize}

@@

\item
  Normal: taking the action prescribed by the protocol.
\item
  Abnormal: everything that deviates from designed steps of the protocol. For example, sending arbitrary message, skipping some step, repeating step, timing out.
\end{enumerate}

Moreover, at any step of the protocol the customer can start a dispute; therefore, another dimension with two positions has to be considered:

@@

\item
  Agree: the customer agree with the action, and therefore does not start a dispute.
\item
  Start a dispute: the customer does not agree with the action and therefore start a dispute.
\end{enumerate}

As a result, in our analysis we have to consider four different outcomes for each party of the protocol:

@@

\item
  $\sigma_\mathrm{n}$: after following the protocol when the other party acted normally.
\item
  $\sigma_\mathrm{d}$: after a settled dispute when the other party acted normally.
\item
  $\sigma_\overline{n}$: after not starting a dispute despite the other party has acted abnormally.
\item
  $\sigma_\overline{d}$: after a settled dispute when the other party has acted abnormally.
\end{itemize}

The protocol terminate after last step, after starting a dispute, or
after a party hasn't completed it's designated action in time. Therefore,
all positions except $\sigma_\mathrm{n}$ are termination positions.

Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer. To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

\begin{definition}[Fairness] \label{fairness}
A protocol achieve fariness iff 
\begin{equation*}
\begin{split}
\forall_{party \in parties}\forall_{\mathrm{step} \in \mathrm{steps}} &\mathrm{can\ move}\\
&\mathrm{to\ the\ non\ disadvantaged\ position} 
\end{split}
\end{equation*}

\end{definition}

@@

For the analysis purpose we state plausable assumptions listed below.

@@

\item
  Both parties start from neutral position (•).
\item
  Both parties, by completing a transaction, end up in advantaged positions (+). In other words, they have intrinsic motivation to initialise and complete the transaction.
\item
  We assume the steps of the protocol to be atomic, there are no
  intermediate steps.
\item
  Repeating the first step starts new transaction. Repeating any other
  step is considered abnormal and gets ignored. For example paying for
  the invoice twice does not cause any effect on the curse of protocol.
\item
  Once published, the results are available to the customer in the
  content storage. The idea of guaranteeing it cryptographically is
  discussed in section ~\ref{future-work}.
\item
  The protocol can go only forward, there is no way of revert any
  action.
\item
  Losing the dispute leads to punishment that is greater than any
  reward, which leads to disadvantaged position (-). Hence, the rational
  customer won't start a dispute that he is not sure to win.
\item
  Winning the dispute leads to neutral position (•).
\item
  Both the customer and the SP are rational (selfish). They always
  prefer go from worst position to better position, but also risk
  temporary worst position in favour for later better position iff it's
  assured that they won't stuck in worst position.
\end{itemize}

@@

\paragraph{Step 1, customer turn: deliver package}\label{step-1-deliver-package}

@@

\paragraph{Step 2, customer turn: pay for invoice}\label{step-2-pay-for-invoice}

@@

\paragraph{Step 3, SP turn: provision of
service}\label{step-3-provision-of-service}

The SP has done the provision of service:

@@

\paragraph{Step 4, SP turn: publication of
results}\label{step-4-publication-of-results}

@@

\paragraph{Step 5, SP turn: publication of
proof-of-provision}\label{step-5-publication-of-proof-of-provision}

The SP has published proof of provision on time:

@@

\paragraph{Step 6, customer turn: pull
proof-of-provision}\label{step-6-pull-proof-of-provision}

@@

\paragraph{Step 7, customer turn: retrieval of
results}\label{step-7-retrieval-of-results}

@@

\subsection{Provable availability of
results}\label{cryptographically-provable-availability-of-results}

Currently, the SP has to publish the results into a p2p content addressable storage network, e.g., IPFS. The problem is that, nothing prevent the SP from publishing the results, receiving the cid, publishing $\mathrm{PoP}$, and immediately after removing the results from the local storage. In case of dispute the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehaviour, other than putting the customer in disadvantaged position caused by the lost dispute. We see possible prevention of this misbehaviour by the usage of Filecoin---an incentive layer on top of IPFS that guarantee the content availability via economic incentivisations~\cite{benetfilecoin}. With the help of Filecoin, the SP would be obligated to create a deal that guarantee the results availability until the deadline of the transaction. Moreover, since Filecoin is a blockchain by itself, it could play both roles of message board and storage network.

@@

Without lose of generality the payment can be made with cash. The customer can exchange the cash with SP together with delivering the package. The $\mathrm{PoD}$ would contain an information that the transaction has been paid with cash; therefore, Steps 1 and 2 could be merged together and realised in one step. In case of dispute the payment disclosure would be in included in $\mathrm{PoD}$.

@@

We assumed the customer to deliver the package to the SP personally or via trusted person. However the system could be extended to support anonymous delivery system as proposed in Lelantos~\cite{altawy2017lelantos}.

\section{Conclusions}
In this paper, we have proposed a anonymity- preserving blockchain-based framework for local services provision. The framework can be employed by any local service provider to provide services without collecting any personal information. The payment is handled by anonymous cryptocurrencies. Proof of delivery and proof of provision are published on message board blockchain. The results are published on content addressable p2p network. The dispute can be settled by disclosing proofs to justice. Assuming the definition~\ref{fairness} we showed that the protocol achieve fairness. Finally, we pinpointed further improvements like decentralised dispute resolution, provable  availability of results, paying with cash, and anonymous delivery via courier.
